---
title: "计量经济学—Stata与R的联系和区别"
author: "LJJ"
date: "2020/4/1"
output:
  html_document:
    highlight: tango
    theme: paper
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*R语言*和*Stata*都是计量经济学研究的神器,一个擅长统计和可视化,一个擅长计量,有很多交叉内容,最好两门都学习,对于计量经济学研究会带来很多方便。网上有很多两个软件的比较,其实对于研究生而言,再讨论软件的优劣毫无意义。但是我个人更喜欢R,毕竟可以写书、搭建网站、搭建博客,数据分析更加强大,和Git、Github更容易联结,现在并行处理使得R速度很快,吐槽速度慢应该还在用for循环吧,`*apply`和`*map`系列多好。Stata在计量经济学独树一帜,很多内置包使得计量学习更加容易,更加专业和有针对性。不管学习哪一个,用心就好,而我喜欢捣鼓,喜欢尝试,就把两者在计量经济学领域的操作进行比较,当然,不可能面面俱到,但入门足矣（窃以为哈哈）

该备忘单总结了用于计量经济学分析的常用Stata命令,并提供了它们在R中的等效表达。

## 1.1 介绍

```
ssc install outreg2
```

```{r}
# install.packages("wooldridge")
# data(package = "wooldridge")
pacman::p_load(margins,AER,fastDummies,lmtest,tidyverse,plm,estimatr,wooldridge)
wage1 %>% DT::datatable()
```

```
browse               // open browser for loaded data
describe             // describe structure of loaded data
summarize            // display summary statistics for all variables in dataset
list in 1/6          // display first 6 rows
tabulate educ        // tabulate `educ` variable frequencies
tabulate educ female // cross-tabulate `educ` and `female` frequencies
```

```{r}
# View(wage1) # open browser for loaded `wage1` data
str(wage1) # describe structure of `wage1` data
```

```{r}
summary(wage1) # display summary statistics for `wage1` variables
```

```{r}
head(wage1) # display first 6 (default) rows data
tail(wage1) # display last 6 rows
```

```{r}
table(wage1$educ) #tabulate `educ` frequencies
table("yrs_edu" = wage1$educ, "female" =wage1$female) # tabulate `educ` frequencies name table columns
```

## 1.2 绘图

```
hist(wage)              // histogram of `wage` hist(wage), by(nonwhite) //
scatter(wage educ)     // scatter plot of `wage` by `educ`
twoway (scatter wage educ) (lfit wage educ) // scatter plot with fitted line
graph box wage, by(nonwhite)                // boxplot of wage by `nonwhite`
```

```{r}
hist(wage1$wage) # histogram of `wage`
```


```{r}
plot(y = wage1$wage, x = wage1$educ) # scatter plot

abline(lm(wage1$wage~wage1$educ),col="red") # add fitted line toscatterplot
```

```{r}
boxplot(wage1$wage~wage1$nonwhite) # boxplot of `wage` by `nonwhite`
```

## 1.3 OLS模型

```
reg wage educ                // simple regression of `wage` by `educ` (Results printed automatically).
reg wage educ if nonwhite==1 // add condition with if statement
reg wage educ exper, robust  // multiple regression using HC1
robust standard errors reg wage educ exper,cluster(numdep) // use clustered standard errors
```

```{r}
mod1 <- lm(wage ~ educ, data = wage1) # simple regression of `wage` by `educ`, store results in `mod1`

summary(mod1) # print summary of `mod1` results

mod2 <- lm(wage ~ educ, data = wage1[wage1$nonwhite==1, ]) # add condition with if statement`

mod3 <- estimatr::lm_robust(wage ~ educ + exper, data = wage1, se_type = "stata") # multiple regression with HC1 (Stata default) robust standard errors, use {estimatr} package

mod4 <- estimatr::lm_robust(wage ~ educ + exper, data = wage1, clusters = numdep) # use clustered standard errors.
```

## 1.4 MLE(Logit/Probit/Tobit)模型

```
logit inlf nwifeinc educ         // estimate logistic regression 
probit inlf nwifeinc educ        // estimate logistic regression
tobit hours nwifeinc educ, ll(0) // estimate tobit regression, lower-limit of y censored at zero
```

```{r}
mod_log <- glm(inlf~nwifeinc + educ,family=binomial(link="logit"), 
               data = mroz) # estimate logistic regression

mod_pro <- glm(inlf~nwifeinc + educ,family=binomial(link="probit"),
               data=mroz) # estimate logistic regression

mod_tob <- AER::tobit(hours ~ nwifeinc + educ, left = 0, 
                      data = mroz) # estimate tobit regression, lower-limit of y censored at zero, use {AER} package
```

## 1.5 生成和编辑变量

```
gen exper2 = exper^2       // create `exper` squared variable
egen wage_avg = mean(wage) // create average wage variable drop tenursq // 
drop `tenursq` variable
keep wage educ exper nonwhite // keep selected variables
tab numdep, gen(numdep)       // create dummy variables for `numdep` recode exper (1/20 = 1 "1 to 20 years") (21/40 = 2 "21 to 40 years") (41/max = 3 "41+ years"),
gen(experlvl) // recode `exper` and gen new variable
```

```{r,eval=FALSE}
wage1$exper2 <- wage1$exper^2 # create `exper` squared variable 

wage1$wage_avg <- mean(wage1$wage) # create average wage variable

wage1$tenursq <- NULL #drop `tenursq`

wage1 <- wage1[ , c("wage", "educ","exper", "nonwhite")] # keep selected variables

wage1 <- fastDummies::dummy_cols(wage1,select_columns = “numdep”) # create dummy variables for `numdep`, use {fastDummies} package

wage1$experlvl <- 3 # recode `exper`

wage1$experlvl[wage1$exper < 41] <- 2

wage1$experlvl[wage1$exper < 21] <- 1 
```

## 1.6 统计检验

```
reg lwage educ exper     // estimation used for examples below 
estat hettest            // Breusch-Pagan / Cook-Weisberg test for heteroskedasticity
estat ovtest             // Ramsey RESET test for omitted variables
ttest wage, by(nonwhite) // independent group t-test, compare means of same variable between
```

```{r}
mod <-lm(lwage ~ educ + exper, data = wage1) # estimate used for examples below

lmtest::bptest(mod) # Breusch-Pagan / Cook-Weisberg test for heteroskedasticity using the {lmtest} package

lmtest::resettest(mod) # Ramsey RESET test

t.test(wage ~ nonwhite, data = wage1) # independent group t-test
```

## 1.8 面板模型

```
xtset id year         // set `id` as entities (panel) and `year` as time variable
xtdescribe            // describe pattern of xt data
xtsum                 // summarize xt data 
xtreg mrdrte unem, fe // fixed effects regression
```

```{r}
plm::is.pbalanced(murder$id,murder$year) # check panel balance with {plm} package
modfe <- plm::plm(mrdrte ~ unem, 
                  index = c("id", "year"),
                  model = "within", 
                  data = murder) # estimate fixed effects (“within”) model
summary(modfe) # display results
```

## 1.8 工具变量

```
ivreg lwage (educ = fatheduc),first // show results of first stage regression
etest first                         // test IV and endogenous variable
ivreg lwage(educ = fatheduc)        // show results of 2SLS directly
```
```{r}
modiv <-AER::ivreg(lwage ~ educ | fatheduc, data = mroz) # estimate 2SLS with {AER} package
summary(modiv, diagnostics = TRUE) # get diagnostic tests of IV and endogenous variable
```

## 1.9 Post-estimation

```
reg wage educ              // estimation used for the following post-estimation commands 
predict yhat               // get predicted values from last estimation, store as `yhat` 
predict e, res             // get residuals from last estimation, store as `e`
```
```{r}
mod1 <- lm(wage ~ educ, data = wage1) # estimation used for the following post-estimation commands
yhat <- predict(mod1) # get predicted values
e <- residuals(mod1) # get residual
```

```
reg lwage educ exper##exper  // estimation used for following postestimation commands
estimates store mod1         // stores in memory the last estimation results to `mod1`
margins                      // get average predictive margins
margins, dydx(*)             // get average marginal effects for all variables
marginsplot                  // plot marginal effects
margins, dydx(exper)         // average marginal effects of experience
margins, at(exper=(1(10)51)) // average predictive margins over `exper` range at 10-year increments
estimates use mod1           // loads `mod1` back into working memory
estimates table mod1 mod2    // display table with stored estimation results
```

```{r}
mod1 <- lm(lwage ~ educ + exper + I(exper^2), data = wage1) # Note: in R, mathematical expressions inside a formula call must be isolated with `I()`

mod1 %>% summary()
```

```{r}
margins::prediction(mod1) # get average predictive margins with {margins} package
```

```{r}
m1 <- margins::margins(mod1) # get average marginal effects for all variables
```

```{r}
plot(m1) # plot marginal effects
```

```{r}
summary(m1) # get detailed summary of marginal effects
```

```{r}
margins::prediction(mod1, at = list(exper = seq(1,51,10))) # predictive margins over `exper` range at 10-year increments
```

```{r}
stargazer::stargazer(mod1, mod2, type = "text") # use {stargazer} package, with `type=text` to display results within R. Note: `type= ` also can be changed for LaTex and HTML output.
```

我也是个小白而已,肯定有疏漏和错误之处,只是最近学习的总结而已。总结和温故不比一直学习新知识不重要,一个人不可能在所有领域都有所涉猎,精通自己的领域已经很难、很难。。。总结、温习和学习一直进行时哈哈。



























