---
title: "Template_Title"
author: 
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. LJJ
date: "`r Sys.Date()`"
output: 
  html_document:
    highlight: espresso
    theme: lumen
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
```

## 加载经常用的R包

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 模型
p_load(tidyverse,grf,glmnet,caret,tidytext,fpp2,
       forecast,car,tseries,hdm,tidymodels,broom)

# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)

# 数据探索
p_load(DT,skimr,DataExplorer,explore,vtable,stringr,lubridate)

# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)

# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

```{r}
library(repurrrsive)
repurrrsive::sw_people %>% listviewer::jsonedit()
```

```{r}
length(sw_people)
sw_people[1]
sw_people[[1]]
sw_people[[1]] %>% class()
```

```{r}
sw_people[[1]][[1]]
str(sw_people,max.level = 1,list.len = 2)
str(sw_people,max.level = 2,list.len = 2)
```

## map函数

```{r}
map(1:10,~.x) 
```

```{r}
map(mtcars,class)
```

```{r}
sw_people[[1]] -> luck
luck %>% class()
luck %>% length()
luck$starships %>% length()
```

```{r}
sw_people[[5]] -> leia
leia$starships %>% length()
```

```{r}
map(sw_people,function(i){   # i传递的是第一个元素
  length(i$starships)
}) %>% unlist()
```

```{r}
planet_lookup <- map_chr(sw_planets, "name") %>%
  set_names(map_chr(sw_planets, "url"))
planet_lookup
```

```{r}
luck$homeworld
luck[[1]]
```

```{r}
planet_lookup[luck$homeworld]
```

```{r}
# How many starships has each character been in?
# names can be useful
sw_people <- sw_people %>% set_names(map_chr(sw_people, "name"))
map(sw_people, ~ length(.x[["starships"]])) %>% unlist()
```

```{r}
map(sw_people,~ .x[["hair_color"]]) %>% unlist()
```

```{r}
map(sw_people, ~ .x[["gender"]] == "male") %>% unlist()
```

```{r}
sw_people %>% listviewer::jsonedit()
```

```{r}
map(sw_people,"name") %>% unlist()
map(sw_people, ~ .x[["name"]]) %>% unlist()

identical(map(sw_people, "name") %>% unlist(),
          map(sw_people, ~ .x[["name"]]) %>% unlist())
```

```{r}
char_starships <- map(sw_people, "starships")

char_starships %>% class()

char_starships %>% listviewer::jsonedit()

char_starships[[2]] %>% length()

map(char_starships,length) %>% unlist()

map(1:length(char_starships), function(i){
  char_starships[[i]] %>% length()
}) %>% unlist()

map(1:length(char_starships), ~ char_starships[[.x]] %>% length()) %>%
  unlist()
```

- Which film (see sw_films) has **the most characters**?
- Which sw_species has **the most possible eye colors**?
- Which sw_planets do we know the least about (i.e. **have the most "unknown" entries**)?

```{r}
str(sw_films,list.len = 3)

sw_films %>% listviewer::jsonedit()

map(sw_films,"characters") %>%
  map(length) %>% 
  unlist() %>% 
  set_names(map_chr(sw_films,"title"))

```

```{r}
sw_species %>% listviewer::jsonedit()

sw_species[[1]] %>% unlist()
```

```{r}
map(sw_species,"eye_colors") %>% 
  str_split(",") %>% 
  map(length) %>% 
  unlist()
```

## walk函数

For functions called for their **side effects**:

- **printing to screen**
- **plotting to graphics device**
- **file manipulation** (saving, writing, moving etc.)
- **system calls**

打印，画图，文件操作

```{r}
walk(1:10,print)
map(1:10,print)
```

## map2函数

```{r}
map2(1:10,1:10,sum) %>% unlist()
```

```{r}
map2(.x = 10, .y = 10, ~rep(1:2,times = .x,each = .y))
```

```{r}
map2(1:10,1:10,function(i,j){
  df <- rnorm(10,mean = i,sd = j)
  return(tibble(df = df))
}) %>% bind_cols()
```

## list columns

```{r}
library(tidyverse)
people_tbl <- tibble(
  name = sw_people %>% map_chr("name"),
  films = sw_people %>% map("films"),
  height = sw_people %>% map_chr("height") %>%
    readr::parse_number(na = "unknown"),
  species = sw_people %>% map_chr("species", .null = NA_character_)
)

people_tbl  # 列表列
```

```{r}
people_tbl$films %>% class()
```

## pmap函数

```{r}
pmap(list(1:10,1:10,1:10),c)
```

pmap( .l , .f , ...)

- .f(.l[[1]][[1]], .l[[2]][[1]], .l[[3]][[1]], ...)
- .f(.l[[1]][[2]], .l[[2]][[2]], .l[[3]][[1]], ...)
- .f(.l[[1]][[3]], .l[[2]][[3]], .l[[3]][[1]], ...)

## invoke_map函数

invoke_map(.f, .x, ...)

- .f[[1]](.x, ...)
- .f[[2]](.x, ...)
- .f[[3]](.x, ...)

```{r}
invoke_map(list(runif, rnorm), n = 5)
```

## 其它函数

purrr provides a pile of functions to make working with them easier

- **Functions**: `safely()`,` possibly()`, `partial()`
- **Lists**: transpose(), `accumulate()`, `reduce()`, every(), order_by()

purrr provides:

- functions that write for loops for you
- with consistent syntax
- convenient shortcuts for specifying functions to iterate

代码简洁、速度更快、语法一致

Choosing the right function depends on:

- type of iteration
- type of output

