--- 
title: "janitor-清洗数据"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    # theme: darkly
    theme: cerulean
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    `janitor` has simple functions for examining and cleaning dirty data. It was built with beginning and intermediate R users in mind and is optimized for user-friendliness. Advanced R users can already do everything covered here, but with `janitor` they can do it faster and save their thinking for the fun stuff.
---

# 加载经常用的R包

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
# bubblyr::bubbly(theme = "sweet")
# bubblyr::bubbly(theme = "rladies")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

# Cleaning dirty data

```{r}
roster_raw <- readxl::read_excel(here::here("R包学习-数据科学/data/dirty_data.xlsx"))
```

```{r}
# roster_raw %>% view()
roster_raw %>% str()
```

```{r}
roster_raw %>% glimpse()
```

```{r}
roster_raw %>% janitor::clean_names()
```
```{r}
roster_raw %>% clean_names() %>% glimpse()
```

```{r}
roster_raw$`Hire Date` %>% excel_numeric_to_date()
```

```{r}
roster_raw %>% clean_names() %>% 
  mutate(hire_date = excel_numeric_to_date(hire_date)) %>% 
  mutate(cert = coalesce(certification_9,certification_10))
```

总结：

- clean_names
- excel_numeric_to_date
- coalesce

# Examining dirty data

## Finding duplicates

Use `get_dupes()` to identify and examine duplicate records during data cleaning. Let’s see if any teachers are listed more than once:

```{r}
iris %>% janitor::get_dupes()
```

```{r}
iris %>% get_dupes(contains("Length")) %>% 
  arrange(-dupe_count)
```

```{r}
roster_raw %>% 
  clean_names() %>% 
  mutate(hire_date = excel_numeric_to_date(hire_date)) %>% 
  mutate(cert = coalesce(certification_9,certification_10)) %>% 
  janitor::remove_empty(which = "rows") -> df
```

```{r}
df %>% 
  tabyl(subject)
```

```{r}
df %>% 
  tabyl(subject,full_time)
```

```{r}
df %>% 
  tabyl(full_time,subject,employee_status,show_missing_levels = FALSE)
```

```{r}
df %>% 
  tabyl(employee_status,full_time) %>% 
  adorn_totals(where = "row") %>% 
  adorn_percentages("row")
```

```{r}
df %>% 
  tabyl(employee_status,full_time) %>% 
  adorn_totals(where = "row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting()
```

```{r}
df %>%
  tabyl(employee_status, full_time) %>%
  adorn_totals(where = "row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns()
```

```{r}
df %>%
  tabyl(employee_status, full_time) %>%
  adorn_totals(where = "row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>% 
  adorn_title("combined")
```

# Reference

- `clean_names()`: Cleans names of an object (usually a data.frame).
- `remove_constant()`: Remove constant columns from a data.frame or matrix.
- `remove_empty()`: Remove empty rows and/or columns from a data.frame or matrix.
- `round_half_up()`: Round a numeric vector; halves will be rounded up, ala Microsoft Excel.
- `signif_half_up()`: Round a numeric vector to the specified number of significant digits; halves will be rounded up.


