---
title: "13工具变量估计"
author: "LJJ"
date: "2020/3/29"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.show = "hold",fig.align = "center")
```

The purpose of this in-class lab13 is to use R to practice with **instrumental variables estimation**. The lab should be completed in your group. To get credit, upload your .R script to the appropriate place on Canvas.

## 13.1 For starters

You may need to install the package `AER`. (It may have already been installed when you previously installed `car` and `zoo`.)

Open up a new R script (named `ICL13_XYZ.R`, where `XYZ` are your initials) and add the usual "preamble" to the top:

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Add names of group members HERE
library(tidyverse)
library(wooldridge)
library(broom)
library(AER)
library(magrittr)
library(stargazer)
```

### 13.1.1 Load the data

We're going to use data on fertility of Botswanian women.

```{r}
df <- as_tibble(fertil2)
df %>% glimpse()
```

### 13.1.2 Summary statistics

We can easily compute summary statistics of our data by using the `stargazer` package:

```{r}
df %>% as.data.frame %>% stargazer(type="text")
```

or:

```{r}
df %>% as.data.frame() %>% skimr::skim()
```

1. What do you think is going on when you see varying numbers of observations across the different variables?

## 13.2 Determinants of fertility

Suppose we want to see if **education causes lower fertility** (as can be seen when comparing more- and less-educated countries):

$$
children = \beta_0 + \beta_1 educ + \beta_2 age + \beta_3 age^2 + u
$$

where $children$ is the number of children born to the woman, $educ$ is years of education, and $age$ is age (in years).

2. Interpret the estimates of the regression:

```{r}
est.ols.rob <- estimatr::lm_robust(children ~ educ + age + I(age^2), data=df)
est.ols <- lm(children ~ educ + age + I(age^2), data=df)
```

```{r}
summary(est.ols)
```

```{r}
summary(est.ols.rob)
```

(Note: include `I(age^2)` puts the quadratic term in automatically without us having to use `mutate()` to create a new variable called `age.sq`.)

We can also use **stargazer** to examine the output. It puts the standard errors of each variable in parentheses under the estimated coefficient.

```{r}
stargazer(est.ols, type="text")
```

### 13.2.1 Instrumenting for endogenous education

**We know that education is endogenous** (i.e. people choose the level of education that maximizes their utility). A possible instrument for education is $firsthalf$, which is a dummy equal to 1 if the woman was born in the first half of the calendar year, and 0 otherwise.

Let's create this variable:

```{r}
df %<>% 
  dplyr::mutate(firsthalf = mnthborn<7)
```

We will assume that $firsthalf$ is uncorrelated with $u$.

3. Check that $firsthalf$ is correlated with $educ$ by running a regression. Call the output `est.iv1`.

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
est.iv1 <- lm(educ ~ firsthalf, data=df)
stargazer(est.iv1, type="text")
```

### 13.2.2 IV estimation

Now let's do the IV regression:

```{r}
est.iv <- ivreg(children ~ educ + age + I(age^2) | firsthalf + age + I(age^2), data=df)
```

```{r}
summary(est.iv)
summary(est.ols)
```

The variables on the right hand side of the `|` are the **instruments** (including the $x$'s that we assume to be exogenous, like $age$). The endogenous $x$ is the first one after the `~`.

Now we can compare the output for each of the models:

```{r}
stargazer(est.ols,est.iv1,est.iv, type="text")
```

4. **Comment on the IV estimates**. Do they make sense? Discuss why the IV standard error is so much larger than the OLS standard error.
