---
title: "14两阶段最小二乘估计(2SLS)"
author: "LJJ"
date: "2020/3/29"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

The purpose of this in-class lab14 is to use R to practice with **two-stage least squares (2SLS) estimation**. The lab14 should be completed in your group. To get credit, upload your .R script to the appropriate place on Canvas.

## 14.1 For starters

Open up a new R script (named `ICL14_XYZ.R`, where `XYZ` are your initials) and add the usual "preamble" to the top:

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Add names of group members HERE
library(tidyverse)
library(wooldridge)
library(broom)
library(AER)
library(magrittr)
library(stargazer)
```

### 14.1.1 Load the data

We're going to use data on **working women.**

```{r}
df <- as_tibble(mroz)
df %>% glimpse()
```

### 14.1.2 Summary statistics

Like last time, let's use `stargazer` to get a quick view of our data:

```{r}
df %>% as.data.frame %>% stargazer(type="text")
```

1. Is it a problem that `wage` and `lwage` have 428 observations, but all of the other variables have 753 observations?

### 14.1.3 Drop missing wages

Using the `filter()` and `is.na()` functions, drop the observations with missing wages. 

```{r include=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
df %<>% 
  dplyr::filter(!is.na(wage))
```

## 14.2 The model

We want to estimate the return to education for women who are working, using mother's and father's education as instruments:

$$
\log(wage) = \beta_0 + \beta_1 educ + \beta_2 exper + \beta_3 exper^2 + u
$$

where $wage$ is the hourly rate of pay, $educ$ is years of education, and $exper$ is labor market experience (in years).

### 14.2.1 First stage regression

Let's estimate the first stage regression, which is a regression of the endogenous variable ($educ$) on the instrument(s) ($motheduc$ and $fatheduc$) and the exogenous explanatory variables ($exper$ and $exper^2$).[^1]

Run this regression. Call the estimation object `est.stage1`.

```{r include=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
est.stage1 <- lm(educ ~ motheduc + fatheduc + exper + I(exper^2), data=df)
```

```{r}
summary(est.stage1)
```

2. Double check that $motheduc$ and $fatheduc$ are jointly significant with an F-stat larger than 10:

```{r}
linearHypothesis(est.stage1,c("motheduc","fatheduc"))
```

### 14.2.2 Second stage regression

In the second stage, we estimate the log wage equation above, but this time we include $\widehat{educ}$ on the right hand side instead of $educ$, where $\widehat{educ}$ are the fitted values from the first stage.

In R, we can easily access the fitted values by typing `fitted(est.stage1)`.

Let's estimate the second stage regression:

```{r}
est.stage2 <- lm(log(wage) ~ fitted(est.stage1) + exper + I(exper^2), data=df)
```

```{r}
summary(est.stage2)
```

### 14.2.3 Both stages at once

The standard errors from the above second stage regression will be incorrect.[^2] Instead, we should estimate these at the same time. We can do this with the `ivreg()` function, just like in the previous lab.

```{r}
est.2sls <- ivreg(log(wage) ~ educ + exper + I(exper^2) | motheduc + fatheduc + exper + I(exper^2), data=df)
```

3. Estimate the OLS model (where $educ$ is not instrumented). Then compare the output for all three models (OLS, 2SLS "by hand", 2SLS "automatic").

```{r include=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
est.ols <- lm(log(wage) ~ educ + exper + I(exper^2), data=df)
```

```{r}
stargazer(est.ols,
          est.stage2,
          est.2sls, type="text")
```

4. Comment on the **IV estimates**. Do they make sense, relative to what we think would bias the returns to education? Is the exogeneity condition on $motheduc$ and $fatheduc$ plausible?

[^1]: Note that you can easily include the quadratic in experience as `I(exper^2)` without having to create this variable in a `mutate()` statement.
[^2]: The reason is that error term in the second stage regression includes the residuals from the first stage, but the standard errors fail to take this into account.





