--- 
title: "slider- “window” based computations"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    theme: darkly
    # theme: cerulean
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    `slider` provides a family of general purpose “`sliding window`” functions. The API is purposefully very similar to `purrr.` The goal of these functions is usually to compute rolling averages, cumulative sums, rolling regressions, or other “window” based computations.
editor_options: 
  chunk_output_type: console
---

# 加载经常用的R包

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
# bubblyr::bubbly(theme = "sweet")
# bubblyr::bubbly(theme = "rladies")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
p_load(slider)
```

# Getting started with slider

## slide()

```{r}
map(1:4,~.x)
```

```{r}
slider::slide(1:4,~.x)
```

On top of this, you can control the size and placement of the window by using the additional arguments to `slide()`. For example, you can ask for a window of size 3 containing “the current element, as well as the 2 before it” like this:

```{r}
slide(1:4,~.x,.before = 2)
```

You’ll notice that **the first two elements of the list contain partial or “incomplete” windows**. By default, `slide()` assumes that you want to compute on these windows anyways, but if you don’t care about them, you can change the `.complete` argument.

```{r}
slide(1:4,~.x,.before = 2,.complete = TRUE)
```

```{r}
slide(1:4,~.x,.before = 1,.after = 1)
```

```{r}
slide(1:4,~.x,.before = Inf)
```

```{r}
slide(1:10,mean,.before = 1,.after = 1)
```

```{r}
slide(1:10,sum,.after = 2)
```

## slide_index()

To make things a bit more interesting, let’s assume that the sales vector from the example above is also tied to some “index”, like a date vector of when the sale actually occurred.

```{r}
index_vec <- as.Date("2019-08-29") + c(0, 1, 5, 6)
wday_vec <- as.character(wday(index_vec, label = TRUE))
wday_vec
```

```{r}
sales_vec <- c(2, 4, 6, 2)

slide_dbl(sales_vec, mean, .before = 2)
```

```{r}
company <- tibble(
  sales = sales_vec,
  index = index_vec,
  wday = wday_vec
)

company
```

```{r}
wday_vec
```

```{r}
slide(wday_vec, ~.x, .before = 2)
```

```{r}
slide_index(wday_vec,index_vec, ~.x, .before = 2)
```

```{r}
slide_index(wday_vec, index_vec, ~.x, .before = days(2))
```

Knowing this, we can swap out `slide_dbl()` for `slide_index_dbl()` to see how to correctly compute our **3 day rolling average**.

```{r}
mutate(
  company,
  roll_val = slide_dbl(sales, mean, .before = 2),
  roll_day = slide_index_dbl(sales, index, mean, .before = days(2))
) -> df

df
```

## slide_period()

With `slide_index()`, we always returned a vector of the same size as .x, and the idea was to build indices to slice .x with using “the current element of .i + some number of elements before/after it”. `slide_period()` works a bit differently. It first breaks .i up into “time blocks” by some period (like monthly), and then uses those blocks to define how to slide over .x.

To see an example, let’s expand out our company sales data frame.

```{r}
big_index_vec <- c(
  as.Date("2019-08-30") + 0:4,
  as.Date("2019-11-30") + 0:4
)
big_index_vec
```

```{r}
big_sales_vec <- c(2, 4, 6, 2, 8, 10, 9, 3, 5, 2)
big_company <- tibble(
  sales = big_sales_vec,
  index = big_index_vec
)
big_company
```

```{r}
slide_period(big_company, big_company$index, "month", ~.x)
```

```{r}
monthly_summary <- function(data) {
  summarise(data, index = max(index), sales = sum(sales))
}

slide_period_dfr(
  big_company,
  big_company$index,
  "month",
  monthly_summary
)
```

```{r}
big_company %>% 
  mutate(index_month = floor_date(index,unit = "month")) %>% 
  group_by(index_month) %>% 
  summarise(sales_sum = sum(sales)) %>% 
  ungroup()
```

or:

```{r}
big_company %>% 
  separate(col = index,into = c("year","month","day")) %>% 
  group_by(year,month) %>% 
  mutate(sales_sum = sum(sales)) %>% 
  ungroup() %>% 
  unite(year:day,col = "date",sep = "-") %>% 
  mutate(date = ymd(date))
```

But here is where things get interesting! Now what if we want to compute those **monthly sales**, but we want the time blocks to be made of the “current month block, **plus 1 month block before it”**. For example, for the month of 2019-09, it would include 2019-08 and 2019-09 together in the rolling summary. There isn’t an easy way to do this in dplyr alone. With slider, there are two ways to do this.

```{r}
slide_period_dfr(
  big_company,
  big_company$index,
  "month",
  monthly_summary,
  .before = 1
)
```

```{r}
big_company %>%
  mutate(
    monthly = floor_date(index, "month"),
    sales_summary = slide_index_dbl(sales, monthly, sum, .before = months(1))
  )
```



















