--- 
title: "purrr教程2"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. LI Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    # theme: darkly
    theme: journal
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# 加载经常用的R包


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE,
                      class.source = "bg-warning")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

```{r}
p_load(repurrrsive,stringi)
```

# 介绍repurrrsive

```{r}
repurrrsive::sw_people %>% listviewer::jsonedit()
sw_people %>% head(2)
sw_people[[1]] 
sw_people[[1]] %>% listviewer::jsonedit()
```

How many elements are in sw_people?

```{r}
sw_people %>% length()
```

Who is the first person listed in sw_people? What information is given for this person?

```{r}
sw_people %>% .[[1]]
```

What is the difference between sw_people[1] and sw_people[[1]]?

```{r}
sw_people %>% .[1]
sw_people %>% .[[1]]
```

# map(.x,.f,...)函数

```{r}
luck <- sw_people[[1]]
luck
luck$starships %>% length()
```

```{r}
leia <- sw_people[[5]]
leia
leia$starships %>% length()
```

```{r}
map(sw_people,function(i){
  i$starships %>% length()
}) %>% unlist()
```

```{r}
map(sw_people,function(i){
  i[["hair_color"]]
}) %>% unlist()
```

```{r}
map(sw_people, "starships") -> x
map(sw_people,function(i){
  i[["starships"]]
}) -> y
all.equal(x,y)
```

为什么要用purrr,而不是apply家族

- consistent return type
- useful shortcuts
- consistent syntax for more complicated iteration

# 轮到你了-sw_*数据集

Which film (see **sw_films**) has the most characters?

```{r}
sw_films %>% listviewer::jsonedit()
sw_films %>% length()
```

```{r}
sw_films %>% .[1]
sw_films %>% .[[1]]
sw_films %>% .[[1]] %>% .[[3]]
```

```{r}
map(sw_films,function(i){
  i[["characters"]]
}) %>% 
  map(length) %>%
  unlist() %>% 
  set_names(
    map_chr(sw_films,function(i){
  i[["title"]]
})
  ) %>% 
  sort()
```

```{r}
sw_species %>% 
  map(function(i){
    i[["eye_colors"]]
  }) %>% unlist() %>% 
  str_split(pattern = ",") %>% 
  map(length) %>% unlist() %>% 
  set_names(1:37) %>% 
  sort()
```

# 更多的迭代函数

- map(.x,.f,...)
- walk(.x,.f,...)
- map2(.x,.y,.f)

# 轮到你了-map or walk

1. For each function, which two arguments might be useful to iterate over?
- download.file()
- rnorm()
- lm()
- predict.lm()
- write.csv()
2. For which functions above should we use walk2() or a typed version of
map2()?

```{r}
gap_split_small <- gap_split[1:10]
countries <- names(gap_split_small)
```

```{r}
ggplot(gap_split[[1]],aes(year,lifeExp)) +
  geom_line() +
  labs(title = countries[[1]]) +
  theme(text = element_text(family = enfont),
        plot.title = element_text(hjust = 0.5))
```

```{r}
map2(gap_split_small,countries,function(i,j){
  ggplot(i,aes(year,lifeExp)) +
  geom_line() +
  labs(title = j) +
  theme(text = element_text(family = enfont),
        plot.title = element_text(hjust = 0.5))
}) -> plots

plots[[2]]
walk(plots,print) # this might take awhile
```

# purrr和列表列

```{r}
people_tbl <- tibble(
  name = sw_people %>% map_chr("name"),
  films = sw_people %>% map("films"),
  height = sw_people %>% map_chr("height") %>%
    readr::parse_number(na = "unknown"),
  species = sw_people %>% map_chr("species", .null = NA_character_
  )
)
people_tbl
```

# purrr：pmap和invoke_map

- pmap
- invoke_map

# WRAP UP!

purrr provides:

- functions that write for loops for you
- with consistent syntax
- convenient shortcuts for specifying functions to iterate

Choosing the right function depends on:

- type of iteration
- type of output

# 学习更多

Jenny Bryan's purrr tutorial

<https://github.com/jennybc/purrr-tutorial>

All materials (code files too): <https://github.com/cwickham/purrr-tutorial>

# 练习1-mtcars

```{r}
mtcars_by_cyl <- mtcars %>% 
  split(mtcars$cyl)
mtcars_by_cyl
```

```{r}
# Fit a regression model to each element 
map(mtcars_by_cyl,function(i){
  lm(mpg~disp,data = i)
})
```

```{r}
library(broom)
# Extract R^2 from each regression model
map(mtcars_by_cyl,function(i){
  lm(mpg~disp,data = i)
}) %>% map(glance) %>% 
  map(function(i){i[["r.squared"]]})
  
```

```{r}
# Extract the slope from each regression model
# Extract R^2 from each regression model
map(mtcars_by_cyl,function(i){
  lm(mpg~disp,data = i)
}) %>% map(tidy) %>% 
  map(function(i){i[["estimate"]]}) %>% 
  bind_cols()
```

# 练习2-word_count.R

```{r}
read_lines(file = "../data1/challenges/word_count_files/geospatial-README.md") -> geospatial_README_text

read_lines(file = "../data1/challenges/word_count_files/nass-README.md") -> nass_README_text

read_lines(file = "../data1/challenges/word_count_files/purrr-workshop-README.md") -> purrr_README_text
```

```{r}
stri_stats_general(geospatial_README_text)
stri_stats_general(nass_README_text)
stri_stats_general(purrr_README_text)
```


