--- 
title: "Higher,further,faster with Marvelous R Markdown"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    theme: darkly
    # theme: cerulean
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
params:
  species: Adelie
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    深入探讨R Markdown的四个分类，进一步领略R Markdown的玄幻之处！四个分类为：Literate Programming，Data Products，Control Documents，Templating。
    
    幻动片：https://docs.google.com/presentation/d/e/2PACX-1vRo1eXJtiwo6aTA8KZ2E-bUbv2GOonC2RIVk_5eWQ5y-ADXbRamBhHaa3w1vMW6BkEPOMJ13ZahSo8Q/embed?start=false&loop=true&delayms=30000&slide=id.p
    
editor_options: 
  chunk_output_type: console
---

# `r emo::ji("smile")`加载经常用的R包`r emo::ji("smile")`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
# bubblyr::bubbly(theme = "sweet")
bubblyr::bubbly(theme = "rladies")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

# `r emo::ji("smile")`Literate Programming`r emo::ji("smile")`

A programming paradigm introduced by `Donald Knuth` in which a computer program is given an explanation of its logic in a natural language, such as English, interspersed with snippets of macros and traditional source code, from which compilable source code can be generated.

```{r, include = TRUE}
p_load(palmerpenguins)
smaller <- penguins %>%
  filter(body_mass_g <= 4000)
```

```{r}
smaller
```

We have data about `r nrow(penguins)` penguins. Only `r nrow(penguins) - nrow(smaller)` are larger than
4000 grams. The distribution of the remainder is shown below:

```{r}
smaller %>% 
  ggplot(aes(body_mass_g)) +
  geom_histogram() +
  mytheme
```

# `r emo::ji("smile")`Data Product`r emo::ji("smile")`

```{r}
p_load(reactable)
```

```{r}
smaller %>% datatable()
```

Data Product(s):

- `Reports` - HTML, PDF, Word, Markdown, RTF, Tufte handout, GitHub document
- `Presentations` - Xaringan, Powerpoint, ioslides, reveal.js, beamer
- `Dashboards` - flexdashboard as standalone or with Shiny
- `Entire websites` - Blogdown, Hugodown, distill, R Markdown site
- `Books` - bookdown
- `HTMLWidgets` - DT, reactable, plotly, crosstalk and more

# `r emo::ji("smile")`Control Document`r emo::ji("smile")`

```{r}
params$species
penguins %>%
  filter(species == params$species) %>%
  filter(!is.na(body_mass_g)) -> smaller
```

We have data about `r nrow(penguins)` penguins. Only `r nrow(penguins) - nrow(smaller)` are not classified as`r params$species`. The distribution of the
`r params$species` penguins are shown below:

```{r}
smaller %>%
  ggplot(aes(body_mass_g,fill = sex)) +
  geom_histogram(binwidth = 100) +
  mytheme
```

# `r emo::ji("smile")`Templating`r emo::ji("smile")`










