--- 
title: "Introduction to labelled"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. LI Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    # theme: darkly
    theme: journal
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# 加载经常用的R包


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

# Variable labels

```{r}
library(labelled)
var_label(iris$Petal.Length) <- "Length of sepal"

var_label(iris) <- list(Petal.Length = "Length of petal",
                        Petal.Width = "Width of Petal")

var_label(iris$Petal.Width)
```

```{r}
var_label(iris)
```

To remove a variable label, use NULL.

```{r}
var_label(iris$Sepal.Length) <- NULL
```

```{r}
# View(iris)
```

可以通过 look for ()显示和搜索变量名和标签:

```{r}
look_for(iris)
look_for(iris,"pet")
```

```{r}
look_for(data = iris,details = TRUE)
```

```{r}
look_for(mtcars,details = TRUE) %>% as_tibble()
```

# Value labels

创建带标签的向量的第一种方法是**使用标签函数**。并不是必须为在矢量中观察到的每个值提供一个标签。您还可以为未观察到的值提供标签。

```{r}
v <- labelled(c(1,2,2,2,3,9,1,3,2,NA), 
              c(yes = 1, no = 3, "don't know" = 8, refused = 9))
v
```

```{r}
val_labels(v)

val_label(v,8)
```

```{r}
val_labels(v) <- c(yes = 1,nno = 3,bug = 5)
v
val_label(v,3) <- "no"
val_label(v,5) <- "bugs"
v
```

```{r}
val_label(v,2) <- "maybe"
v
```

```{r}
val_labels(v) <- NULL
v
```

```{r}
val_label(v,1) <- "yes"
v
```

Note that applying `val_labels` to a factor will *have no effect*!!

```{r}
f <- factor(1:3,levels = 1:3)
f

val_labels(f) <- c(yes = 1,no = 2,bug = 3)
f
```

You could also apply value labels to several columns of a data frame.

```{r}
df <- data.frame(v1 = 1:3, v2 = c(2, 3, 1), v3 = 3:1)
df
```

```{r}
val_label(df, 1) <- "yes"
df
```

```{r}
look_for(df,details = TRUE)
df$v1 <- haven::as_factor(df$v1)
df
```

```{r}
df <- data.frame(v1 = 1:3, v2 = c(2, 3, 1), v3 = 3:1)

val_label(df, 1) <- "yes"
val_label(df[, c("v1", "v3")], 2) <- "maybe"
val_label(df[, c("v2", "v3")], 3) <- "no"
val_labels(df)
```

# Sorting value labels

```{r}
v <- c(1,2,2,2,3,9,1,3,2,NA)
v
val_label(v,1) <- "yes"
val_label(v,3) <- "no"
val_label(v,9) <- "refused"
val_label(v,2) <- "maybe"
val_label(v,8) <- "don't know"
v
```

It could be useful to reorder the **value labels** according to their attached values.

```{r}
sort_val_labels(v)
sort_val_labels(v,decreasing = TRUE)
sort_val_labels(v,according_to = "l")
```

# User defined missing values (SPSS’s style)

```{r}
v <- labelled(c(1,2,2,2,3,9,1,3,2,NA),
              labels = c(yes = 1,no = 3,"don't know" = 9))
v
```

```{r}
na_values(v) <- 100
na_values(v)
v
```

```{r}
is.na(v)
```

# Converting to factor

```{r}
v <- labelled(c(1,2,2,2,3,9,1,3,2,NA),
              c(yes = 1, no = 3, "don't know" = 8, refused = 9))
v
v %>% to_factor()
```

```{r}
to_factor(v,levels = "v")
to_factor(v,levels = "p")
```

# Other type of conversions

```{r}
v
to_character(v)
```

# Conditionnal conversion to factors(重要)

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
df <- data.frame(
  a = labelled(c(1, 1, 2, 3), labels = c(No = 1, Yes = 2)),
  b = labelled(c(1, 1, 2, 3), labels = c(No = 1, Yes = 2, DK = 3)),
  c = labelled(c(1, 1, 2, 2), labels = c(No = 1, Yes = 2, DK = 3)),
  d = labelled(c("a", "a", "b", "c"), labels = c(No = "a", Yes = "b")),
  e = labelled_spss(
    c(1, 9, 1, 2), 
    labels = c(No = 1, Yes = 2),
    na_values = 9
    )
)
df %>% glimpse()
```

```{r}
unlabelled(df)
```

```{r}
df %>% haven::as_factor(levels = "l")
```

```{r}
unlabelled(df,drop_unused_label = TRUE)
```

```{r}
p_load(questionr)
data(fertility)
glimpse(women)
```

```{r}
women$residency %>% sample(10)
```

```{r}
women
```

```{r}
women %>% unlabelled()
```

```{r}
glimpse(women %>% mutate(across(is.labelled %>% where(), to_factor)))
```

```{r}
women %>% mutate(across(employed:religion,to_factor))
```
